### 2019-04-02 Introduction.tex
sections 3-4 fixes

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each timestep $t$ puts different weights on different words (features) and thus effectively attends on a list of important words. The context vector $c_t$ is computed as the weighted average over the dense representation of these words to capture information from the document. The context $c_t$, the RNN memory $h_t$ at timestep $t$, and the previous label ${s_{t-1}}$ are concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(c_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

>>>>

At prediction time, one seeks to find the sequence with the highest probability $\mathbf{s}^*=\arg\max_\mathbf{s} p(\mathbf{s}|x)$, and this is usually implemented approximately with a beam search procedure \cite{lowerre1976harpy} (we modified into Algorithm \ref{alg:beam_combine}). The sequence history is encoded with an internal memory vector $h_t$ which is updated over time. RNN is also often equipped with the attention mechanism \cite{DBLP:journals/corr/BahdanauCB14}, which in each timestep $t$ puts different weights on different words (features) and thus effectively attends on a list of important words. The context vector $c_t$ is computed as the weighted average over the dense representation of these words to capture information from the document. The context $c_t$, the RNN memory $h_t$ at timestep $t$, and the encoding of previous label ${s_{t-1}}$ are all concatenated and used to model the label probability distribution at time $t$ as $p(s_t|x,s_1,s_2,...,s_{t-1}) \sim  \softmax(\phi(c_t,h_t,s_{t-1}))$, where $\phi$ is a non-linear function, and $\softmax$ is the normalized exponential function generalizing binary logistic regression. %Other variants of RNN, such as sequence to sequence encoder-decoder structure \cite{DBLP:conf/emnlp/ChoMGBBSB14,DBLP:conf/nips/NamMKF17}, further take into account the word order in the documents. \kechen{remove last sentence?}

### 2019-04-02 Model.tex
sections 3-4 fixes

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure \cite{rumelhart1988learning} (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$.   
  % \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. }
  To be precise, our label ``permutations'' $\pi$ are sequences that allow repetitions (i.e.\ $(y_1,y_2,y_3,y_1,...)$), up to a maximum length. So the set probability sums over all such permutations, and both training and prediction candidate sets are generated this way. In practice, we do not think this detail makes any difference, as sequences with repeated labels are extremely rare; however in theory we want to allow the attention context to focus on any recent labels it chooses to (repeated if necessary).

@@

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. 
Using Jensen’s inequality, one can show that the total probability mass in Eq. 3 will be less than or equal to the true amount of probability mass in Eq. 1. In this sense, previous work is optimizing a bound on the log-likelihood, while we are optimizing it directly.

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up sequence (permutation) probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set. Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

>>>>

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure \cite{rumelhart1988learning} (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$.   
  % \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. }
  To be precise, our label ``permutations'' $s$ are sequences that allow repetitions (i.e.\ $(y_1,y_2,y_3,y_1,...)$), up to a maximum length. So the set probability sums over all such permutations, and both training and prediction candidate sets are generated this way. In practice, we do not think this detail makes any difference, as sequences with repeated labels are extremely rare; however in theory we want to allow the attention context to focus on any recent labels it chooses to (repeated if necessary).

@@

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. 
Using Jensen’s inequality, one can show that the total probability mass of the objective in Eq. 3 is less than or equal to the true amount of probability mass (Eq. 5); In this sense, previous work is optimizing a bound on the log-likelihood, while we are optimizing it directly.

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up sequence (permutation) probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set. Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). The ``ALL'' flag determines if the sequences can terminate with a partial subset of labels (as called in Algorithm 3 line 2 ) or a full set is required (as called in Algorithm 3 line 7 and Algorithm 2 line 4). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

### 2019-04-02 results.tex
sections 3-4 fixes

\subsection{Experimental Results}

@@

Our method performs the best in all metrics on all datasets. All RNN based methods perform better than traditional methods BR, BR-support and PCC. Among the Vinyals-RNN variants, Vinyals-RNN-max and Vinyals-sample work the best and have similar performance. However, they have to be initialized by Vinyals-RNN-uniform. Otherwise, the training gets stuck in early stage and the performance degrades significantly. One can see the clear degradation by comparing the Vinyals-RNN-max row (with initialization) with the Vinyals-RNN-max-direct row (without initialization). By contrast, our training objective in set-RNN does not suffer from this issue and can serve as a stable stand alone training objective.

@@

Next we analyze how much benefit our new set prediction strategy brings in. For each RNN-based method, we test two prediction strategies: 1) finding the sequence with the highest probability and outputting the corresponding set (this is the default prediction strategy for all models except set-RNN); 2) outputting the set with the \kechen{approximated} highest probability (this is the default prediction strategy for set-RNN). Table~\ref{table_prediction} shows how each method performs with these two prediction strategies. One can see that Vinyals-RNN-uniform and set-RNN benefit most from predicting the top set,  Vinyals-RNN-sample, Vinyals-RNN-max and Vinyals-RNN-max-direct benefit less, and seq2seq RNN does not benefit at all. Intuitively, for the top-set prediction to be different from the top-sequence prediction, the model has to spread probability mass across different sequence permutations of the same set.

This motivates us to check how sharply (or uniformly) distributed the probabilities are over different sequence permutations of the predicted set. We first normalize these sequence probabilities related to the predicted set and then compute the entropy. To make predictions with different set sizes (and hence different number of sequence permutations) comparable, we further divide the entropy by the logarithm of number of sequences. Smaller entropy values indicate a sharper distributions. The results are shown in Figure~\ref{fig:entropy}.

>>>>

\subsection{Experimental Results}
% \kechen{split this section into subsections?}

% \kechen{I have a slight concern about the scalability of this approach, both with varying beam size and number of labels. I'm curious about the computational complexities of the training and prediction methods provided in the Algorithm 2 and Algorithm 3 and how that compares with existing methods.}

@@

Our method performs the best in all metrics on all datasets (except hamming loss on AAPD, see table \ref{table3}). All RNN based methods perform better than traditional methods BR, BR-support and PCC. Among the Vinyals-RNN variants, Vinyals-RNN-max and Vinyals-sample work the best and have similar performance. However, they have to be initialized by Vinyals-RNN-uniform. Otherwise, the training gets stuck in early stage and the performance degrades significantly. One can see the clear degradation by comparing the Vinyals-RNN-max row (with initialization) with the Vinyals-RNN-max-direct row (without initialization). By contrast, our training objective in set-RNN does not suffer from this issue and can serve as a stable stand alone training objective.

@@

Next we analyze how much benefit our new set prediction strategy brings in. For each RNN-based method, we test two prediction strategies: 1) finding the sequence with the highest probability and outputting the corresponding set (this is the default prediction strategy for all models except set-RNN); 2) outputting the set with the highest approximated probability (this is the default prediction strategy for set-RNN). Table~\ref{table_prediction} shows how each method performs with these two prediction strategies. One can see that Vinyals-RNN-uniform and set-RNN benefit most from predicting the top set,  Vinyals-RNN-sample, Vinyals-RNN-max and Vinyals-RNN-max-direct benefit less, and seq2seq RNN does not benefit at all. Intuitively, for the top-set prediction to be different from the top-sequence prediction, the model has to spread probability mass across different sequence permutations of the same set.

\subsection{Analysis: Sequence Probability Dsitribution}
This motivates us to check how sharply (or uniformly) distributed the probabilities are over different sequence permutations of the predicted set. We first normalize these sequence probabilities related to the predicted set and then compute the entropy. To make predictions with different set sizes (and hence different number of sequence permutations) comparable, we further divide the entropy by the logarithm of number of sequences. Smaller entropy values indicate a sharper distributions. The results are shown in Figure~\ref{fig:entropy}.
